\begin{recipe}{Mac \& Cheese}{Helen Voysey}{1 hour}
  \ing{}{elbow macaroni}
  \ing{8 oz.}{extra-sharp cheddar}
  \ing{\fr13 cup}{margarine}
  \ing{}{garlic powder}
  \ing{}{onion powder}
  \ing{}{basil}
  \ing{}{black pepper}
  \ing{3 Tbsp}{white flour}
  \ing{1 cup}{milk}

  Grate the cheddar. Boil the macaroni until it's a little chewy (no longer
  crunchy). While that's boiling, liquify the margerine. Once it's clear, add
  the garlic powder, onion powder, basil, ground pepper, and flour. Heat for a
  few minutes so the flour absorbs the grease. Add the milk. Mix this
  vigorously so that it doesn't get lumpy. You'll end up with a spice gravy.

  Mix the gravy in with the cooked macaroni. Alternate layers of this mixture
  with layers of cheese in a casserole dish, starting with the macaroni and
  ending with cheese. Sprinkle some bread crumbs on top, and put a few pats of
  margerine. Bake at 350\0F for about a half hour.
\end{recipe}
{\it The above is a very ad-hoc recpie, so there are a lot of substitutions
  that can be made. Real garlic can be used instead of the powdered kind; in
  this case, use a teaspoon. Real onion can be used instead of the powder; it
  should be sauteed in the margarine until it's clear. Butter can be used
  instead of margerine.

  Notes from Ian/V: 1 lb of pasta fills two pyrexes, and we used slightly more
  cheese and a little more flour. Paprika + chili flakes + garlic + salt in the
  gravy, cooked down white button mushroom and spinach works well.}
