\documentclass{book}
\usepackage[nonumber,index]{cuisine}
\usepackage[bookmarks=true,colorlinks=true]{hyperref}
\title{Collected Voysey \& Co. Recipes}
\author{Ian Voysey}

\begin{document}
\maketitle
\tableofcontents
\chapter{Chicken}
\begin{recipe}{Beer Can Chicken}{Mel Hunter}{3 hours}
  \ing[$n$]{whole}{chickens}
  \ing[$n$]{cans}{beer}
  
  Throughly clean chickens. Open and insert one can of beer into each
  bird, and grill in a tray for 2 hours, or until golden brown.
\end{recipe}

\begin{recipe}{Chicken Cacciatore}{Lea}{1 hour}
  \ing[$1$]{clove}{garlic}
  \ing{}{olive oil}
  \ing{}{chicken breasts}
  \ing[$1$]{can}{crushed tomatoes}
  \ing{}{basil}
  \ing{}{oregano}
  \ing{}{cumin}
  \ing{}{salt \& pepper}

  Heat a small amount of olive oil in a deep pan. Fry the garlic in the oil,
  being careful not to burn it. Brown both sides of the chicken in the same
  pan. Put in the crushed tomatoes, mixing with water so that the chicken is
  totally covered. Add spices to taste. Bring the whole mixture to a boil, put
  a lid on it, and let it simmer for a half hour. Serves well with rice.
\end{recipe}

\begin{recipe}{Berber Chicken}{GEV}{3 hours}
  \ing[1]{whole}{chicken}
  \ing[1-2]{fresh}{lemons}
  \ing[2]{tsp}{ground cumin}
  \ing[1]{tsp}{tumeric}
  \ing[1]{tsp}{ginger}
  \ing[2]{tsp}{paprika}
  \ing[\fr12]{tsp}{garlic}
  \ing[\fr12]{tsp}{cinnamon}
  \ing[\fr12]{tsp}{pepper}
  \ing[1]{tsp}{salt}
  \ing[\fr12]{tsp}{cayanne}
  
  Throughly clean chicken. Stuff with quartered lemons. Oil and spice rub the
  whole outside. Bake uncovered at 425\0F until done and crispy.
\end{recipe}

\chapter{Beef}
\begin{recipe}{Meatballs}{Helen Voysey}{1 hour}
  \ing{1.5 lbs}{lean ground beef}
  \ing{\fr13 cups}{bread cumbs}
  \ing{1}{egg}
  \ing{}{basil}
  \ing{}{parsley}
  \ing{}{garlic powder}
  \ing{}{onion powder}
  \ing{}{milk}

  Mix the above throughly, using enough milk to absorb into the bread
  crumbs. Make the meatballs not too big, and don't pack them tightly. Put
  them on a broiler pan, baking at 350\0F until brown. 
\end{recipe}

\chapter{Pork}
\begin{recipe}{Weiner Schnizel}{Anca Diana Dr\u{a}gan}{20 mins}
  \ing[$n$]{whole}{pork cutlets}
  \ing{}{eggs}
  \ing{}{bread crumbs}
  \ing{}{frying oil}
  
  Beat the cutlets with a meat hammer until thin. Dredge the cutlets first in
  egg, then bread crumbs. Fry in oil. Goes will with boiled potatoes.
\end{recipe}
\begin{recipe}{Mustard Pork Chops}{Helen Voysey}{20 mins}
  \ing[2]{whole}{pork chops}
  \ing[1\fr12]{Tbs}{white wine}
  \ing[1]{Tbs}{oil}
  \ing{}{salt \& pepper}
  \ing[1]{Tbs}{parsley}
  \ing[1]{Tbs}{dijon mustard}
  \ing{}{frying oil}
  \ing{}{fresh mushroom caps}

  Mix wine, measured oil, salt, pepper, and mustard. Smear mixture over chops
  and leave for one hour. Preheat oil in a frying pan, and cook chops for 5
  minutes per side. Add mushroom caps and parsley, cover, and cook until
  mushrooms are tender.
\end{recipe}
\chapter{Fish}
\begin{recipe}{Very Simple Salmon}{Helen Voysey}{20 Mins}
  \ing[$n$]{}{salmon steaks}
  \ing{}{rosemary}
  \ing{}{olive oil}

  Clean salmon. Drench in oil, and liberally sprinkle with rosemary
  leaves. Grill for about 5 mins on the scale side, and 2 mins on the spiced
  side, until done.
\end{recipe}
\textit{This preparation goes profoundly well with Corsendonk Abbey Brown
  Ale.}
\chapter{Casseroles}
\begin{recipe}{Mac \& Cheese}{Helen Voysey}{1 hour}
  \ing{}{elbow macaroni}
  \ing{8 oz.}{extra-sharp cheddar}
  \ing{\fr13 cup}{margarine}
  \ing{}{garlic powder}
  \ing{}{onion powder}
  \ing{}{basil}
  \ing{}{black pepper}
  \ing{3 Tbsp}{white flour}
  \ing{1 cup}{milk}

  Grate the cheddar. Boil the macaroni until it's a little chewy (no longer
  crunchy). While that's boiling, liquify the margerine. Once it's clear, add
  the garlic powder, onion powder, basil, ground pepper, and flour. Heat for a
  few minutes so the flour absorbs the grease. Add the milk. Mix this
  vigorously so that it doesn't get lumpy. You'll end up with a spice gravy.

  Mix the gravy in with the cooked macaroni. Alternate layers of this mixture
  with layers of cheese in a casserole dish, starting with the macaroni and
  ending with cheese. Sprinkle some bread crumbs on top, and put a few pats of
  margerine. Bake at 350\0F for about a half hour.
\end{recipe}
{\it The above is a very ad-hoc recpie, so there are a lot of substitutions
  that can be made. Real garlic can be used instead of the powdered kind; in
  this case, use a teaspoon. Real onion can be used instead of the powder; it
  should be sauteed in the margarine until it's clear. Butter can be used
  instead of margerine.}


\chapter{Sauces and Marinades}
\chapter{Vegetable}
\begin{recipe}{Bean Thing}{Hayley Finley}{20 Mins}
  \ing{}{black-eyed peas}
  \ing{}{onion}
  \ing{}{diced green chilies}
  \ing{}{garlic}

  Soak the beans in cold water with a the vinegar over night. Cook as
  indicated on the package, adding other things as desired. Goes very well
  with Spanish style rice and corn bread.
\end{recipe}

\chapter{Deserts \& Baked Goods}
\begin{recipe}{Cornbread}{Moosewood Cookbook}{Half hour}
  \ing[1]{cup}{unbleached flour}
  \ing[1]{cup}{yellow corn meal}
  \ing[2]{tsp}{baking powder}
  \ing[\fr12]{tsp}{baking soda}
  \ing[\fr12]{tsp}{salt}
  \ing[3]{tbsp}{melted margarine}
  \ing[1]{cup}{buttermilk}
  \ing[\fr14]{cup}{honey}
  \ing{1}{large egg}

  Beat together egg, buttermilk, and honey in a large bowl. Mix the
  dry ingredients together. Combine the dry and wet ingredients with
  the melted margarine. Spread batter into a greased 8" square pan,
  and bake for twenty minuets (or until golden brown) at 425\0F for
  twenty minutes.
\end{recipe}
\textit{ It's easy to add things to this batter, such as jalape\~no
  peppers, whole corn, onions, or candied ginger.}

\begin{recipe}{Molasses Ginger Cookies}{Jillifer's Emporium}{25 Hours}
  \ing[1]{pound}{butter}
  \ing[2]{cups}{brown sugar}
  \ing[0.25]{cups}{water}
  \ing[1.5]{teaspoon}{salt}
  \ing[0.75]{cup}{molasses}
  %%%%% step 
  \ing[3]{large}{eggs}
  %%%%% step 
  \ing[6.5]{cups}{flour}
  \ing[1]{tablespoon}{baking soda}
  \ing[1]{tablespoon}{cinnamon}
  \ing[2]{teaspoons}{cloves}
  \ing[2.25]{teaspoons}{ginger}

  Cream butter, brown sugar, water, salt, and molasses. Beat in eggs one at a
  time. Sift remaining dry ingredients together and add the creamed
  mixture. Mix well. Cover and refrigerate for twenty-four hours. Roll in to
  balls approximately 2" in diameter. Flatten slightly on to cookie
  sheet. Bake at 350\0F for 15-18 minutes.
\end{recipe}
\textit{The brown sugar can be substituted for 2 cups of white sugar, or .75
  cups of honey as desired. Blackstrap honey can be used instead of molasses}

\begin{recipe}{Gingerbread Scones}{Jillifer's Emporium}{1 Hour}
  \ing[2]{cups}{unbleached flour}
  \ing[3]{Tbs}{brown sugar}
  \ing[2]{tsp}{baking powder}
  \ing[\fr12]{tsp}{baking soda}
  \ing[\fr12]{tsp}{salt}
  \ing[1]{tsp}{ground ginger}
  \ing[\fr12]{tsp}{cinnamon}
  \ing[\fr14]{cup}{cold margarine}
  \ing[\fr13]{cup}{molasses}
  \ing[\fr14]{cup}{milk}
  \ing[1]{large}{egg, separated}

  In a large bowl, combine the flour, brown sugar, baking powder,
  ginger, baking soda, salt, and cinnamon. Cut in margarine until
  mixture resembles coarse meal. In a small bowl, combine the
  molasses, milk, and egg yolk until smooth. Stir into the flour mix
  until just moistened. Turn out on to a floured surface, and knead
  6-8 times. Pat into a round mound about 8" in diameter. Cut into 12
  wedges, and place them on a baking sheet. Beat egg whites until
  frothy, and brush over wedges. Sprinkle with sugar. Bake for 12-15
  mins, or until golden brown, at 400\0F.
\end{recipe}

\begin{recipe}{Apple Pie Filling}{Sara Swift}{1.5 Hours}
  \ing[7-8]{large}{tart apples (Empire, Cortland)}
  \ing[1]{tsp}{cinnamon}
  \ing[\fr12]{tsp}{allspice}
  \ing[\fr14]{cup}{unbleached flour}
  \ing[\fr13]{cup}{sugar}
  \ing[2]{tsp}{lemon juice}
  \ing[1]{Tbsp}{butter}
  \ing{few oz.}{milk}
  
  Peel and slice apples. Toss the apple slices with lemon
  juice. Combine all dry ingredients. Toss apples with flour mixture,
  and let stand for 10-15 mins. Pour apple mixture in to the pie
  shell, shaving in butter before the top crust. Moisten the rim of
  the bottom crust with water, place on the top crust, fold under, and
  crimp. Brush top crust with milk, and sprinkle with sugar. Cut 6 or
  so heat vents in the top crust. Wrap the outer edge of the crust
  with an aluminium collar. Bake at 425\0F for 50 mins, or until
  golden brown.
\end{recipe}
\textit{One may use as much as one-third of a cup of flour, and
  one-half of a cup of sugar, to taste}

\begin{recipe}{Standard Pie Crust}{Helen Voysey}{10 minuets}
  \ing[1]{cup}{unbleached flour}
  \ing[\fr12]{tsp}{salt}
  \ing[1\fr13]{tbsp}{hard shortening}
  \ing[2-3]{\textit{cold}}{club soda or seltzer}

  Mix the salt and flour. Cut Shortening into the flour mixture until no
  longer visible; it should resemble coarse meal. Add club soda to this
  1 Tbsp at a time. The dough should be pliable and easy to manage,
  and you can adjust that by adding more club soda. Roll out on to a
  floured sheet of wax paper. Peel paper off the back as you drape
  dough over your arm.
\end{recipe}
\textit{If you are making a double crust, do not attempt to double
  these numbers. Make two separate batches. This crust fits an 8 or 9
  inch pie pan.}

\begin{recipe}{All-Purpose Scones}{SCA Mirriam}{20 Mins}
  \ing[1]{lb}{flour}
  \ing[2]{tbsp}{sugar}
  \ing[4]{tsp}{baking powder}
  \ing[\fr14]{tsp}{salt}
  \ing[1]{stick}{softened butter}
  \ing[5]{oz}{currants}
  \ing[$\leq$10]{oz}{milk}

  Optionally, wet and briefly heat currants to plump them. Add
  together dry ingredients and currants. With a fork, add in butter
  until evenly distributed. Add milk in 2 oz increments, slowly
  stirring. Stop once all the dry ingredients have been absorbed;
  dough should be pliable, but still pretty wet and sticky. Split
  dough in half, and mush each half in to a flattened cylinder. Cut 6
  isosceles wedges from each. Bake at 450\0F for 10 mins, or until
  golden brown.
\end{recipe}
\textit{Note that most anything can be used instead of currants:
  walnut halves; dried cherries, blueberries, or cranberries; cinnamon
  chips; \&c.}

\begin{recipe}{Beer Bread}{Graham Voysey}{1 Hour}
  \ing[12]{oz}{beer}
  \ing[3]{cups}{self-rising flour}
  \ing[3]{tbsp}{sugar}

  In a large bowl,  mix together sugar and flour. Add beer and continue to
  mix, first with a wooden spoon, then hands. Pour into a $9\times 5$ greased
  loaf pan. Bake at 350 for 50 to 60 minutes. The top should be crunchy.
\end{recipe}
\textit{An excellent way to dispose of unwanted beer. Works very differently
  with different beers: Victory Moonglow isn't at all bad, Penn Pilsner is
  very fluffy; most stouts are heavy and bitter.}


\begin{recipe}{Bran Muffins}{Helen Voysey}{1.5 Hours}
  \ing[3]{cups}{wheat bran}
  \ing[\fr12]{cups}{margerine}
  \ing[1]{cups}{boiling water}
  \ing[1]{cups}{milk}
  \ing[1]{cups}{yogurt}
  \ing[2]{}{eggs}
  \ing[2 \fr12]{cups}{flour}
  \ing[1]{cups}{sugar}
  \ing[1 \fr12]{tsp}{baking powder}
  \ing[1 \fr12]{tsp}{baking soda}
  \ing[1]{tsp}{salt}

  Cut margerine into bran until seedy. Add water until melted and
  mixed. Combine milk, yogurt, and eggs into mix. Stir in baking soda, powder,
  and salt. Add sugar, then lastly mix in the flour.
\end{recipe}

\textit{This mix will last upto four weeks in a sealed container in the
  fridge.}

\chapter{Alcohol}
\begin{recipe}{Irish Cream}{SCA Cordials; Graham Voysey}{1 weeks}
  \ing[3]{large}{eggs, beaten}
  \ing[1]{pint}{heavy whipping cream}
  \ing[1]{can}{sweetened condensed milk}
  \ing[1]{tbsp}{honey}
  \ing[1]{tbsp}{chocolate syrup}
  \ing[1]{cup}{Jameson's Whiskey}
  
  Mix eggs, condensed milk, and cream throughly. Add honey and chocolate to
  taste. Add the whiskey last. Mix until totally smooth, taking care to whip
  the fat in the cream. You must age the cream for at least a week in the
  fridge; it must always be kept cold. You should shake it daily to ensure
  that it stays well mixed.
\end{recipe}

\textit{See \underline{Joy of Cooking} chocolate syrup recipe. Damn shame to
  use something like Hershey's after all that work.}

\begin{recipe}{Jo Bartley's Christmas Punch}{Kingsley Amis}{20 mins}
  \ing[3]{bottles}{dry or medium-dry white wine}
  \ing[2]{bottles}{dry gin}
  \ing[1]{bottle}{brandy}
  \ing[1]{bottle}{sherry}
  \ing[1]{bottle}{dry vermouth}
  \ing[5]{quarts}{medium-sweet cider}
  \ing{}{ice}

  If you feel like throwing the unfinished drinks from last night, nobody will
  notice. Mix everything together and serve from jugs that have some ice in
  them. Remember GP4 and cut all the corners you can: Spanish white, cocktail
  gin, non-cognac but not non-French brandy, British sherry and British
  vermouth; the cider will cover them and blend them into a splendid new
  whole. Despite the potency that lurks behind its seeming mildness, I have
  never known anybody to suffer while or after drinking it.
\end{recipe}

\begin{recipe}{Gl\"{o}gg}{SCA Cordials}{1 hour}
  \ing[2]{bottles}{wine}
  \ing[2]{bottles}{port}
  \ing[1]{bottle}{brandy}
  \ing[2]{orange}{peels}
  \ing[2]{cups}{sugar}
  \ing{}{clove}
  \ing{}{cinnamon}
  \ing{}{cadamom}
  \ing{}{nutmeg}
  \ing{}{black pepper}
  \ing{}{almonds or rasins \textit{(optional)}}

  Heat in a slow cooker or on the stove, keeping it below boiling.

\end{recipe}
\end{document}
