\begin{recipe}{Vincent Standard Glop}{Vincent Zeng}{A few hours}

    \ing[1]{lb.}{ground turkey}
    \ing[1]{diced}{onion}
    \ing[3]{diced}{bell peppers}
    \ing[2]{diced}{russet potatoes}
    \ing[5-10]{cloves}{minced garlic}
    \ing[2]{lbs.}{navy or great northern beans}
    \ing[1-3]{tbsp.}{red chili flakes}
    \ing[1-3]{tbsp.}{salt}
    \ing[2-5]{tbsp.}{chicken powder}
    \ing[1]{sprinkling}{fennel, cumin, paprika}

    Soak the beans overnight with a splash of vinegar.

    Heat some cooking oil in a large (10 qt.?) stock pot; gently sautee the
    onion and chili flakes until the oil starts to color, before the garlic
    starts to brown. Brown the turkey with some salt and black pepper. Toss in
    onion and bell peppers and let it cook down gently, about 5-7 minutes. Toss
    in potatoes, then give everything 5-10 minutes to get acquainted. Stir well.
    Add in the spices as you're feeling up to it. Once everything's warm and
    making little noises, drain the beans and dump them in, then add water to
    cover, plus maybe an inch or so, depending on how watery you want this. Turn
    that heat up high to get it to a simmer, then let it sit on low for a while.
    Do your dishes. Clean the table. Read a book. Taste it once in a while, and
    add salt if needed. Once the beans are mushy, pull it off the heat and stir
    firmly while it cools down. The more you stir, the starchier it gets.

    Put some in the freezer for later. This will feed two people every night for
    a couple weeks, probably.

\end{recipe}

\it{Spices are, as usual, flexible and to taste.}
